---
  title: "Figure3_Adaptation_to_(n, PVE, SignalShape)"
  output:
    workflowr::wflow_html:
    code_folding: hide
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Source Code

```{r library, message = FALSE}
library(Matrix); library(ggplot2); library(cowplot); library(susieR); library(BGLR);
library(glmnet); library(mr.ash.alpha); library(ncvreg); library(L0Learn); library(varbvs);
standardize = FALSE
source('code/method_wrapper.R')
source('code/sim_wrapper.R')
```

## Scenarios

### Scenario 7

Scenario 7 (Varying $n$): $n \in [\textrm{200}, \textrm{5,000}]$, $p = \textrm{2,000}$, $s = \textrm{20}$, $\textrm{Design} = \textrm{IndepGauss}$, $\textrm{PVE} = 0.5$ and $\textrm{SignalShape} = \textrm{PointNormal}$.

```{r code8, eval = FALSE}
tdat8        = list()
n_range      = c(200,500,1000,2000,5000,10000,20000,50000)
p            = 2000
s            = 20
method_list  = c("varbvs","bayesb","blasso","susie","enet","lasso","ridge","scad2","mcp2","l0learn")
method_list2 = c("mr.ash", method_list)
method_num   = length(method_list2)
iter_num     = 20
pred         = matrix(0, iter_num, method_num); colnames(pred) = method_list2
time         = matrix(0, iter_num, method_num); colnames(time) = method_list2

for (iter in 1:5) {
  n               = n_range[iter]
for (i in 1:20) {
  
  data          = simulate_data(n, p, s = s, seed = i, signal = "normal", pve = 0.5)
  
  for (j in 1:length(method_list)) {
    fit.method    = get(paste("fit.",method_list[j],sep = ""))
    fit           = fit.method(data$X, data$y, data$X.test, data$y.test, seed = i)
    pred[i,j+1]   = fit$rsse / data$sigma / sqrt(n)
    time[i,j+1]   = fit$t
    
    if (method_list[j] == "lasso") {
      pred[i,method_num - 1] = fit$rsse2 / data$sigma / sqrt(n)
    } else if (method_list[j] == "enet") {
      pred[i,method_num - 2] = fit$rsse2 / data$sigma / sqrt(n)
    } else if (method_list[j] == "ridge") {
      pred[i,method_num - 0] = fit$rsse2 / data$sigma / sqrt(n)
    }
  }
 
  fit         = fit.mr.ash(data$X, data$y, data$X.test, data$y.test, seed = i,
                           sa2 = (2^((0:19) / 20) - 1)^2)
  pred[i,1]   = fit$rsse / data$sigma / sqrt(n)
  time[i,1]   = fit$t
  
  print(c(time[i,]), digits = 4)
  print(c(pred[i,]), digits = 4)
}
  print("-----------------------------------")
  tdat8[[iter]] = data.frame(pred = c(pred), time = c(time), fit = rep(method_list2, each = 20))
}
```

### Scenario 8

Scenario 8 (Varying PVE): $n = \textrm{500}$, $p = \textrm{2,000}$, $s = \textrm{20}$, $\textrm{Design} = \textrm{IndepGauss}$, $\textrm{PVE} = \in [0,0.9]$ and $\textrm{SignalShape} = \textrm{PointNormal}$.

```{r code9, eval = FALSE}
tdat9        = list()
n            = 500
p            = 2000
pve_range    = seq(0,0.9,0.1)
s            = 20
method_list  = c("varbvs","bayesb","blasso","susie","enet","lasso","ridge","scad2","mcp2","l0learn")
method_num   = length(method_list) + 1
iter_num     = 20
pred         = matrix(0, iter_num, method_num); colnames(pred) = c("mr.ash", method_list)
time         = matrix(0, iter_num, method_num); colnames(time) = c("mr.ash", method_list)

for (iter in 1:10) {
for (i in 1:20) {
  data          = simulate_data(n, p, s = s, seed = i, signal = "normal", pve = pve_range[iter])
 
  for (j in 1:length(method_list)) {
    fit.method    = get(paste("fit.",method_list[j],sep = ""))
    fit           = fit.method(data$X, data$y, data$X.test, data$y.test, seed = i)
    pred[i,j+1]   = fit$rsse / data$sigma / sqrt(n)
    time[i,j+1]   = fit$t
  }
 
  fit         = fit.mr.ash(data$X, data$y, data$X.test, data$y.test, seed = i,
                           sa2 = (2^((0:19) / 20) - 1)^2)
  pred[i,1]   = fit$rsse / data$sigma / sqrt(n)
  time[i,1]   = fit$t
  print(pred[i,])
}
tdat9[[iter]] = data.frame(pred = c(pred), time = c(time), fit = rep(c("mr.ash", method_list), each = 20))
}
```

### Scenario 9

Scenario 9 (Varying SignalShape with a dense signal): $n = \textrm{500}$, $p = \textrm{200}$, $s = \textrm{200}$, $\textrm{Design} = \textrm{IndepGauss}$ and $\textrm{PVE} = 0.5$. We sample $\beta$ from the point-$h$ density, i.e.
\ba
\beta_j = \left\{ \begin{array}{ll} \iid\, h, & j \in S \\
= 0, & j \notin S \end{array} \right,
\ea
for $h \in \{t_1,t_2, t_4, t_8, \mathcal{L}(1), \mathcal{N}(0,1), \mathcal{U}(-1,1),\mathcal{C}(1) \}$, where $t_{\rm df}$ is the $t$-density with degree of freedom df, and $\mathcal{L}$, $\mathcal{N}$, $\mathcal{U}$ and $\mathcal{C}$ denote Laplace, Normal, Uniform and Constant densities, respectively. Again, $\beta$ is rescaled after sampling to satisfy $\textrm{PVE} = 0.5$.

```{r code10, eval = FALSE}
tdat10       = list()
n            = 500
p            = 200
s            = 200
method_list  = c("varbvs","bayesb","blasso","susie","enet","lasso","ridge","scad2","mcp2","l0learn")
method_list2 = c("mr.ash", method_list, "enet2","lasso2","ridge2")
method_num   = length(method_list2)
iter_num     = 20
pred         = matrix(0, iter_num, method_num); colnames(pred) = method_list2
time         = matrix(0, iter_num, method_num); colnames(time) = method_list2

for (iter in 1:8) {
  df           = c(1,2,4,8)
  signal_shape = c("lap","normal","unif","const")
for (i in 1:20) {
  
  if (iter <= 4) {
    data          = simulate_data(n, p, s = s, seed = i, signal = "t", df = df[iter], pve = 0.5)
  } else if (iter > 4) {
    data          = simulate_data(n, p, s = s, seed = i, signal = signal_shape[iter - 4], pve = 0.5)
  }

  for (j in 1:length(method_list)) {
    fit.method    = get(paste("fit.",method_list[j],sep = ""))
    fit           = fit.method(data$X, data$y, data$X.test, data$y.test, seed = i)
    pred[i,j+1]   = fit$rsse / data$sigma / sqrt(n)
    time[i,j+1]   = fit$t
    
    if (method_list[j] == "lasso") {
      pred[i,method_num - 1] = fit$rsse2 / data$sigma / sqrt(n)
    } else if (method_list[j] == "enet") {
      pred[i,method_num - 2] = fit$rsse2 / data$sigma / sqrt(n)
    } else if (method_list[j] == "ridge") {
      pred[i,method_num - 0] = fit$rsse2 / data$sigma / sqrt(n)
    }
  }
 
  fit         = fit.mr.ash(data$X, data$y, data$X.test, data$y.test, seed = i,
                           sa2 = (2^((0:19) / 20) - 1)^2)
  pred[i,1]   = fit$rsse / data$sigma / sqrt(n)
  time[i,1]   = fit$t
  print(c(pred[i,]), digits = 4)
}
  tdat10[[iter]] = data.frame(pred = c(pred), time = c(time), fit = rep(method_list2, each = 20))
}
```

### Scenario 10

Scenario 10 (Varying SignalShape with a sparse signal): $n = \textrm{500}$, $p = \textrm{2,000}$, $s = \textrm{20}$, $\textrm{Design} = \textrm{IndepGauss}$, $\textrm{PVE} = 0.5$ and varying signal shapes described in Scenario 9.

```{r code11, eval = FALSE}
tdat11        = list()
n            = 500
p            = 2000
s            = 20
method_list  = c("varbvs","bayesb","blasso","susie","enet","lasso","ridge","scad2","mcp2","l0learn")
method_list2 = c("mr.ash", method_list, "enet2","lasso2","ridge2")
method_num   = length(method_list2)
iter_num     = 20
pred         = matrix(0, iter_num, method_num); colnames(pred) = method_list2
time         = matrix(0, iter_num, method_num); colnames(time) = method_list2

for (iter in 1:8) {
  df           = c(1,2,4,8)
  signal_shape = c("lap","normal","unif","const")
for (i in 1:20) {
  
  if (iter <= 4) {
    data          = simulate_data(n, p, s = s, seed = i, signal = "t", df = df[iter], pve = 0.5)
  } else if (iter > 4) {
    data          = simulate_data(n, p, s = s, seed = i, signal = signal_shape[iter - 4], pve = 0.5)
  }

  for (j in 1:length(method_list)) {
    fit.method    = get(paste("fit.",method_list[j],sep = ""))
    fit           = fit.method(data$X, data$y, data$X.test, data$y.test, seed = i)
    pred[i,j+1]   = fit$rsse / data$sigma / sqrt(n)
    time[i,j+1]   = fit$t
    
    if (method_list[j] == "lasso") {
      pred[i,method_num - 1] = fit$rsse2 / data$sigma / sqrt(n)
    } else if (method_list[j] == "enet") {
      pred[i,method_num - 2] = fit$rsse2 / data$sigma / sqrt(n)
    } else if (method_list[j] == "ridge") {
      pred[i,method_num - 0] = fit$rsse2 / data$sigma / sqrt(n)
    }
  }
 
  fit         = fit.mr.ash(data$X, data$y, data$X.test, data$y.test, seed = i,
                           sa2 = (2^((0:19) / 20) - 1)^2)
  pred[i,1]   = fit$rsse / data$sigma / sqrt(n)
  time[i,1]   = fit$t
  print(c(pred[i,]), digits = 4)
}
  tdat11[[iter]] = data.frame(pred = c(pred), time = c(time), fit = rep(method_list2, each = 20))
}
```

## Save the results

```{r saveresults}
saveRDS(tdat8, "results/scenario7.RDS")
saveRDS(tdat9, "results/scenario8.RDS")
saveRDS(tdat10, "results/scenario9.RDS")
saveRDS(tdat11, "results/scenario10.RDS")
```