---
title: "Home"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

## Build Info

To build this vignette.

```{r build}
library(workflowr);
wflow_publish("analysis/index.Rmd")
```

## Package Info

For package version and information, see `Session Information` at the end of this documentation.

```{r package-info, message = FALSE, echo = TRUE, warning = FALSE}
library(mr.ash.alpha); # package implementing proposed methods in the paper
library(Matrix); library(mvtnorm) # miscellaneous packages for matrices
library(glmnet); library(ncvreg); library(L0Learn); # penalized regression methods
library(varbvs); library(susieR); library(BGLR); # Bayesian methods
library(ggplot2); library(cowplot); # plotting
```

## Tutorial for the Repository

```{r tutorial}
source('code/method_wrapper.R')
source('code/sim_wrapper.R')
```

## Reproduce the results for the paper

To reproduce the results in the paper, run the following code.

You need to install `workflowr` R package, or replace `workflowr::wflow_publish` by `rmarkdown::render`.

```{r run-simulation, message = FALSE, echo = TRUE, warning = FALSE, eval = FALSE}
filelist          = paste("analysis/", list.files("analysis", pattern = "*_Sourcecode.Rmd"), sep = "")
for (i in 1:length(filelist)) {
  workflowr::wflow_publish(filelist[i])
  cat("file",i,": ",'"',filelist[i],'"'," is published\n",sep = "")
}
```

## Create Figures in the paper

To generate figures in the paper, run the following code.

You need to have results from the code in the above chunk.

```{r create-plot, message = FALSE, echo = TRUE, warning = FALSE, eval = FALSE}
filelist          = paste("analysis/", list.files("analysis", pattern = "*_Plot.Rmd"), sep = "")
for (i in 1:length(filelist)) {
  workflowr::wflow_publish(filelist[i])
  cat("file",i,": ",'"',filelist[i],'"'," is published\n",sep = "")
}
```

## Session Information

The below is for providing R version and package information.

```{r session-info}
sessionInfo()
```