---
title: "Home"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

## Build Info

To build this vignette, run

`workflowr::wflow_publish("analysis/index.Rmd")` or `rmarkdown::render("analysis/index.Rmd")`

from your R console.

```{r build, message = FALSE, echo = TRUE, warning = FALSE}
library(workflowr);
```

## Package Info

For package version and information, see `Session Information` at the end of this documentation.

```{r package-info, message = FALSE, echo = TRUE, warning = FALSE}
library(mr.ash.alpha); # package implementing proposed methods in the paper
library(Matrix); library(mvtnorm) # miscellaneous packages for matrices
library(glmnet); library(ncvreg); library(L0Learn); # penalized regression methods
library(varbvs); library(susieR); library(BGLR); # Bayesian methods
library(ggplot2); library(cowplot); # plotting
```

## Tutorial for the Repository

First, load the main functions.

```{r tutorial}
source('code/method_wrapper.R')
source('code/sim_wrapper.R')
```

One can generate the data as follows.

```{r generate-data}
data = simulate_data(n = 100, p = 200, s = 5,
                     design = "indepgauss", # "equicorrgauss",
                     signal = "normal", # "lap", "t", etc.
                     pve = 0.5)
str(data)
```

One can run each method by calling the wrapper. For instacne, for fitting `mr.ash` simply call `fit.mr.ash`.

```{r run-method}
method_list  = c("mr.ash","varbvs","bayesb","blasso","susie","enet","lasso","ridge","scad2","mcp2","l0learn")
fit.function = get(paste0("fit.", method_list[1], sep = ""))

fit          = fit.function(data$X, data$y, data$X.test, data$y.test)
```

Each `fit.function` runs under the default setting of each method.

It can accept non-default argument, for instance, `fit.susie(..., L = 20)`.

## Reproduce the results for the paper

To reproduce the results in the paper, run the following code.

You need to install `workflowr` R package, or replace `workflowr::wflow_publish` by `rmarkdown::render`.

In `analysis` folder of the repository, `*_Sourcecode.Rmd` files (e.g. Figure2_Sourcecode1.Rmd) contain source codes.

Each `*_Sourcecode.Rmd` file requires minutes/hours/days to be rendered by MacBook Pro (15-inch, 2016) 2.6 GHz Intel Core i7 16GB RAM.

```{r run-simulation, message = FALSE, echo = TRUE, warning = FALSE, eval = FALSE}
filelist          = paste("analysis/", list.files("analysis", pattern = "*_Sourcecode.Rmd"), sep = "")
for (i in 1:length(filelist)) {
  workflowr::wflow_publish(filelist[i])
  cat("file",i,": ",'"',filelist[i],'"'," is published\n",sep = "")
}
```

## Create Figures in the paper

To generate figures in the paper, run the following code.

You need to have results from the code in the above chunk.

```{r create-plot, message = FALSE, echo = TRUE, warning = FALSE, eval = FALSE}
filelist          = paste("analysis/", list.files("analysis", pattern = "*_Plot.Rmd"), sep = "")
for (i in 1:length(filelist)) {
  workflowr::wflow_publish(filelist[i])
  cat("file",i,": ",'"',filelist[i],'"'," is published\n",sep = "")
}
```

## Session Information

The below is for providing R version and package information.

```{r session-info}
sessionInfo()
```