---
title: "Result3_SignalShape"
output:
  workflowr::wflow_html:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This .Rmd file is to plot results for the experiment MR.ASH and the comparison methods listed below.

(1) `glmnet` R package: Ridge, Lasso, E-NET
(2) `ncvreg` R package: SCAD, MCP
(3) `L0Learn` R package: L0Learn
(4) `BGLR` R package: BayesB, Blasso (Bayesian Lasso)
(5) `susieR` R package: SuSiE (Sum of Single Effect)
(6) `varbvs` R package: VarBVS (Variational Bayes Variable Selection)

The experiment is based on the following simulation setting.

### Design setting

We use 20 real genotype matrices from GTEx consortium (https://gtexportal.org/home/).

$n = 287$ and $p = 5732, 7659, 6857, 4012, 6356, 8683, 4076, 7178, 4847, 5141, 6535, 7537, 7263, 7011, 7468, 5020, 8760, 5995, 6440, 5456$. The number of coefficients $p$ varies from 4,012 to 8,760. The average size of $p$ is 6,401.3.

Also, columns of $X$ are very highly correlated (even some are perfectly correlated).

### Signal setting

We will use the following 6 different signal settings with the same sparsity $s = 20$.

(1) SparseLaplace: $\beta_j \sim \textrm{Laplace}(1)$ for $j \in J$ and $\beta_j = 0$ otherwise, where $J$ is a set of randomly $s$ indices in $\{1,\cdots,p\}$, chosen uniformly at random.

(2) SparseT2: $\beta_j \sim \textrm{t}_2$ for $j \in J$ and $\beta_j = 0$ otherwise, where $J$ is a set of randomly $s$ indices in $\{1,\cdots,p\}$, chosen uniformly at random.

(3) SparseT5: $\beta_j \sim \textrm{t}_5$ for $j \in J$ and $\beta_j = 0$ otherwise, where $J$ is a set of randomly $s$ indices in $\{1,\cdots,p\}$, chosen uniformly at random.

(4) SparseNormal: $\beta_j \sim N(0,\sigma_\beta^2)$ for $j \in J$ and $\beta_j = 0$ otherwise, where $J$ is a set of randomly $s$ indices in $\{1,\cdots,p\}$, chosen uniformly at random.

(5) SparseUniform: $\beta_j \sim \textrm{Unif}(0,1)$ for $j \in J$ and $\beta_j = 0$ otherwise, where $J$ is a set of randomly $s$ indices in $\{1,\cdots,p\}$, chosen uniformly at random.

(6) SparseConstant: $\beta_j = 1$ for $j \in J$ and $\beta_j = 0$ otherwise, where $J$ is a set of randomly $s$ indices in $\{1,\cdots,p\}$, chosen uniformly at random.

The following is the tail behaviors of the above signal generating probability distributions.

```{r tail, message = FALSE}
library(ggplot2); library(cowplot)
x = seq(-100,100,0.01)
dat = rbind(data.frame(x = x, y = dexp(abs(x), 1, log = TRUE) / 2, signal = "SparseLaplace"),
            data.frame(x = x, y = dt(x, df = 2, log = TRUE), signal = "SparseT2"),
            data.frame(x = x, y = dt(x, df = 5, log = TRUE), signal = "SparseT5"),
            data.frame(x = x, y = dnorm(x, log = TRUE), signal = "SparseNormal"))
ggplot(dat) + geom_line(aes(x = x, y = y, color = signal)) + 
  coord_cartesian(ylim = c(-50,0)) + theme_cowplot(font_size = 14) +
  theme(axis.line    = element_blank()) +
  labs(x = "x", y = "logpdf(x)")
```

### PVE

Then we sample $y = X\beta + \epsilon$, where $\epsilon \sim N(0,\sigma^2 I_n)$.

We fix PVE = 0.99, where PVE is the proportion of variance explained, defined by

$$
{\rm PVE} = \frac{\textrm{Var}(X\beta)}{\textrm{Var}(X\beta) + \sigma^2},
$$
where $\textrm{Var}(a)$ denotes the sample variance of $a$ calculated using R function `var`. To this end, we set $\sigma^2 = \textrm{Var}(X\beta)$.

When PVE is large, then it implies that the signal-to-noise ratio (SNR) is also large. Usually SNR is defined as

$$
{\rm SNR} = \frac{\textrm{Var}(X\beta)}{\sigma^2} = \frac{PVE}{1- PVE} = \frac{1}{(PVE)^{-1} - 1}
$$
Thus large PVE implies large SNR. When SNR is large, we expect that the cross-validated $\lambda$ and the VEB estimate $g$ are both fairly accurate, and thus one can directly compare the flexibility of the shrinkage operator.

### Performance Measure

The above two figures display the prediction error. The prediction error we define here is

$$
\textrm{Pred.Err}(\hat\beta;y_{\rm test}, X_{\rm test}) = \frac{\textrm{RMSE}}{\sigma} = \frac{\|y_{\rm test} - X_{\rm test} \hat\beta \|}{\sqrt{n}\sigma}
$$

where $y_{\rm test}$ and $X_{\rm test}$ are test data sample in the same way. If $\hat\beta$ is fairly accurate, then we expect that $\rm RMSE$ is similar to $\sigma$. Therefore in average $\textrm{Pred.Err} \geq 1$ and the smaller the better.

### Packages / Libraries

A list of packages we have loaded is collapsed. Please click "code" to see the list.

```{r library, message = FALSE}
library(Matrix); library(ggplot2); library(cowplot); library(susieR); library(BGLR);
library(glmnet); library(varbvs2); library(ncvreg); library(L0Learn); library(varbvs);
standardize = FALSE
source('code/method_wrapper.R')
source('code/sim_wrapper.R')
```

## Results 

```{r fig1, fig.height=13, fig.width=15}
res_df       = readRDS("results/signalshape_pve0.99.RDS")
method_list  = c("Mr.ASH","VarBVS","BayesB","Blasso","SuSiE","E-NET","Lasso","Ridge","SCAD","MCP","L0Learn")
method_level = c("Mr.ASH","E-NET","Lasso","Ridge",
                 "SCAD","MCP","L0Learn",
                 "VarBVS","BayesB","Blasso","SuSiE")
col          = gg_color_hue(11)
for (i in 1:6) {
res_df[[i]]$fit   = rep(method_list, each = 20)
res_df[[i]]$fit   = factor(res_df[[i]]$fit, levels =  c("Mr.ASH","E-NET","Lasso","Ridge",
                                            "SCAD","MCP","L0Learn",
                                            "VarBVS","BayesB","Blasso","SuSiE"))
some              = c(1,2,3,5,6,7)
res_df[[i]] = res_df[[i]][res_df[[i]]$fit %in% method_level[some],]
}
pp = list()
signal_name = c("SparseLaplace","SparseT2","SparseT5","SparseNormal","SparseUnif","SparseConst")
for (i in 1:6) {
  d       = res_df[[i]]
  pp[[i]] = my.box(d, "fit", "pred", values = col[some]) +
  theme(axis.line    = element_blank(),
        axis.text.x  = element_text(angle = 45,hjust = 1),
        legend.position = "none") +
  geom_hline(yintercept = median(d$pred[d$fit == "Mr.ASH"]), col = col[1],
             linetype = "dotted", size = 1.5) +
  scale_y_continuous(trans = "log10", breaks = c(1,1.2,1.4,1.6,1.8,2.0)) +
  coord_cartesian(ylim = c(0.95,1.8))
  subtitle  = ggdraw() + draw_label(paste(paste("Signal: ",signal_name[i], sep = ""),"", sep = ""),
                                    fontface  = 'bold', size = 18)
  pp[[i]]   = plot_grid(subtitle, pp[[i]], ncol = 1, rel_heights = c(0.06,0.95))
}
fig_main  = plot_grid(pp[[1]],pp[[2]],pp[[3]],pp[[4]],pp[[5]],pp[[6]], nrow = 2, rel_widths = c(0.3,0.3,0.3,0.3))
title     = ggdraw() + draw_label("Prediction Error (log-scale)", fontface = 'bold', size = 20) 
subtitle  = ggdraw() + draw_label("Scenario: LowdimIndepGauss, n = 500, p = 2000, s = 20, pve = 0.99", fontface = 'bold', size = 18)
fig       = plot_grid(title,subtitle,fig_main, ncol = 1, rel_heights = c(0.04,0.06,0.95))
fig
```

```{r fig2, fig.height=7, fig.width=15}
sdat = rbind(res_df[[1]], res_df[[2]], res_df[[3]], res_df[[4]], res_df[[5]], res_df[[6]])
p1       = my.box(res_df[[1]], "fit", "time", values = gg_color_hue(11)[c(1,3,7,6,9,11,2,4,5,8)]) +
  theme(axis.line    = element_blank(),
        axis.text.x  = element_text(angle = 45,hjust = 1),
        legend.position = "none") +
  scale_y_continuous(trans = "log10")
p0        = ggplot() + geom_blank() + theme_cowplot() + theme(axis.line = element_blank())
fig_main  = plot_grid(p0,p1,p0, nrow = 1, rel_widths = c(0.6,0.6,0.6))
title     = ggdraw() + draw_label("Computation time (log-scale)", fontface = 'bold', size = 20) 
subtitle  = ggdraw() + draw_label("Scenario: IndepGauss + SparseSignals, n = 500, p = 2000, s = 20, pve = 0.99", fontface  = 'bold', size = 18) 
fig       = plot_grid(title,subtitle,fig_main, ncol = 1, rel_heights = c(0.1,0.06,0.95))
fig
```

## Source code

The source code will be popped up when you click `code` on the right side. 

```{r code, eval = FALSE}
tdat1        = list()
n            = 500
p            = 2000
s            = 20
signal_list  = c("lap","t2","t5","normal","unif","const")
method_list  = c("varbvs","bayesb","blasso","susie","enet","lasso","ridge","scad","mcp","l0learn")
method_num   = length(method_list) + 1
iter_num     = 20
pred         = matrix(0, iter_num, method_num); colnames(pred) = c("mr.ash", method_list)
time         = matrix(0, iter_num, method_num); colnames(time) = c("mr.ash", method_list)

for (iter in 1:6) {
for (i in 1:20) {
  data          = simulate_data(n, p, s = s, seed = i, signal = signal_list[iter], pve = 0.99)


 
  for (j in 1:length(method_list)) {
    fit.method    = get(paste("fit.",method_list[j],sep = ""))
    fit           = fit.method(data$X, data$y, data$X.test, data$y.test, seed = i)
    pred[i,j+1]   = fit$rsse / data$sigma / sqrt(n)
    time[i,j+1]   = fit$t
  }
 
  fit         = fit.mr.ash(data$X, data$y, data$X.test, data$y.test, seed = i,
                           sa2 = (2^((0:19) / 5 / sqrt(2)^(iter-1)) - 1)^2)
  pred[i,1]   = fit$rsse / data$sigma / sqrt(n)
  time[i,1]   = fit$t
}
}
tdat1[[iter]] = data.frame(pred = c(pred), time = c(time), fit = rep(c("mr.ash", method_list), each = 20))
```

## System Configuration

Click the below Session Info.