---
title: "Result4_Highdim"
output:
  workflowr::wflow_html:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This .Rmd file is to plot results for the experiment MR.ASH and the comparison methods listed below.

(1) `glmnet` R package: Ridge, Lasso, E-NET
(2) `ncvreg` R package: SCAD, MCP
(3) `L0Learn` R package: L0Learn
(4) `BGLR` R package: BayesB, Blasso (Bayesian Lasso)
(5) `susieR` R package: SuSiE (Sum of Single Effect)
(6) `varbvs` R package: VarBVS (Variational Bayes Variable Selection)

The experiment is based on the following simulation setting.

### Design setting

We sample the standard i.i.d. Gaussian measurement $X_{ij} \sim N(0,1)$ anda construct $X \in \mathbb{R}^p$ with $n = 500$ and $p = 50,500,5000,50000$.

### Signal setting

We sample the i.i.d. normal coefficients $\beta_j \sim N(0,\sigma_\beta^2)$ for $j \in J$ and $\beta_ j = 0$ otherwise, where $J$ is a set of randomly $s$ indices in $\{1,⋯,p\}$c hosen uniformly at random.

This signal will be called `sparsenormal`.

We will fix $s = 20$ throughout this experiment.

### PVE

Then we sample $y = X\beta + \epsilon$, where $\epsilon \sim N(0,\sigma^2 I_n)$.

We fix PVE = 0.5, where PVE is the proportion of variance explained, defined by

$$
{\rm PVE} = \frac{\textrm{Var}(X\beta)}{\textrm{Var}(X\beta) + \sigma^2},
$$
where $\textrm{Var}(a)$ denotes the sample variance of $a$ calculated using R function `var`. To this end, we set $\sigma^2 = \textrm{Var}(X\beta)$.

### Performance Measure

The above two figures display the prediction error. The prediction error we define here is

$$
\textrm{Pred.Err}(\hat\beta;y_{\rm test}, X_{\rm test}) = \frac{\textrm{RMSE}}{\sigma} = \frac{\|y_{\rm test} - X_{\rm test} \hat\beta \|}{\sqrt{n}\sigma}
$$
where $y_{\rm test}$ and $X_{\rm test}$ are test data sample in the same way. If $\hat\beta$ is fairly accurate, then we expect that $\rm RMSE$ is similar to $\sigma$. Therefore in average $\textrm{Pred.Err} \geq 1$ and the smaller the better.

### Packages / Libraries

A list of packages we have loaded is collapsed. Please click "code" to see the list.

```{r library, message = FALSE}
library(Matrix); library(ggplot2); library(cowplot); library(susieR); library(BGLR);
library(glmnet); library(varbvs2); library(ncvreg); library(L0Learn); library(varbvs);
standardize = FALSE
source('code/method_wrapper.R')
source('code/sim_wrapper.R')
```

## Results

The result is summarized below. 

```{r fig1, fig.height=7, fig.width=15}
res_df       = readRDS("results/highdim_pve0.5.RDS")
method_list  = c("Mr.ASH","VarBVS","BayesB","Blasso","SuSiE","E-NET","Lasso","SCAD","MCP","L0Learn")
method_level = c("Mr.ASH","E-NET","Lasso",
                 "SCAD","MCP","L0Learn",
                 "VarBVS","BayesB","Blasso","SuSiE")
col          = gg_color_hue(11)[-8]
shape        = c(19,4,5,7,8,17,24,25,9,3,11)[-8]
p_list       = c(50,500,5000,50000)
sdat         = data.frame()
for (i in 1:4) {
  sdat = rbind(sdat, data.frame(pred = colMeans(matrix(res_df[[i]]$pred, 20, 10)),
                                time = colMeans(matrix(res_df[[i]]$time, 20, 10)),
                                fit  = method_list,
                                p = p_list[i]))
}
sdat$fit = factor(sdat$fit, levels = method_level)

p1 = ggplot(sdat) + geom_line(aes(x = p, y = pred, color = fit)) +
  geom_point(aes(x = p, y = pred, color = fit, shape = fit), size = 2.5) +
  theme_cowplot(font_size = 14) +
  scale_x_continuous(trans = "log10", breaks = p_list) +
  labs(y = "predictior error (rmse / sigma)", x = "number of coefficients (p)") +
  theme(axis.line = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  scale_color_manual(values = col) +
  scale_shape_manual(values = shape) +
  scale_y_continuous(trans = "log10")
p1
```

## Source code

The source code will be popped up when you click `code` on the right side. 

```{r code, eval = FALSE}
tdat1        = list()
n            = 500
p_range      = c(50,500,5000,50000)
s            = 20
method_list  = c("varbvs","bayesb","blasso","susie","enet","lasso","scad2","mcp2","l0learn")
method_num   = length(method_list) + 1
iter_num     = 20
pred         = matrix(0, iter_num, method_num); colnames(pred) = c("mr.ash", method_list)
time         = matrix(0, iter_num, method_num); colnames(time) = c("mr.ash", method_list)


for (iter in 1:4) {
for (i in 1:20) {
  data          = simulate_data(n, p_range[iter], s = s, seed = i, signal = "normal", pve = 0.5)
 
  for (j in 1:length(method_list)) {
    fit.method    = get(paste("fit.",method_list[j],sep = ""))
    fit           = fit.method(data$X, data$y, data$X.test, data$y.test, seed = i)
    pred[i,j+1]   = fit$rsse / data$sigma / sqrt(n)
    time[i,j+1]   = fit$t
  }
 
  fit         = fit.mr.ash(data$X, data$y, data$X.test, data$y.test, seed = i,
                           sa2 = (2^((0:19) / 20) - 1)^2)
  pred[i,1]   = fit$rsse / data$sigma / sqrt(n)
  time[i,1]   = fit$t
}
tdat1[[iter]] = data.frame(pred = c(pred), time = c(time), fit = rep(c("mr.ash", method_list), each = 20))
}
```