---
title: "Result11_UpdateOrder"
output:
  workflowr::wflow_html:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This .Rmd file is to plot results for the experiment of MR.ASH's internal setting.

A list of update orders we consider is as follows.

(1) `random`: In each outer loop iteration, we sample a permuation map $\xi:\{1,\cdots,p\} \to \{1,\cdots,p\}$ uniformly at random and run inner loop iterations with the order based on $\xi$.

(2) `increasing`: $(1,\cdots,p)$, i.e. in each outer loop iteration, we update $q_1,q_2,\cdots,q_p$ in this order.

(3) `lasso.pathorder`: we update $q_j$ prior to $q_{j'}$ when $\beta_j$ appears earlier than $\beta_{j'}$ in the lasso path. If ties occur, then `increasing` order applies to those ties.

(4) `scad.pathorder`: we update $q_j$ prior to $q_{j'}$ when $\beta_j$ appears earlier than $\beta_{j'}$ in the scad path. If ties occur, then `increasing` order applies to those ties.

(5) `lasso.absorder`: we update $q_j$ prior to $q_{j'}$ when the lasso solution satisfies $\hat\beta_j \geq \hat\beta_{j'}$. If ties occur, then `increasing` order applies to those ties.

(6) `univar.absorder`: we update $q_j$ prior to $q_{j'}$ when the univariate linear regression solution satisfies $\hat\beta_j \geq \hat\beta_{j'}$. If ties occur, then `increasing` order applies to those ties.

### Design setting

We sample the equicorrelated Gaussian measurement $X_{ij} \sim N(0,\Sigma)$ where $\Sigma$ has diagonal entries $1$ and off-diagonal entries $\rho$. 

The we construct $X \in \mathbb{R}^p$ with $n = 500$ and $p = 2000$.

### rho

We will use $\rho = 0.95$. In this case, MR.ASH with a default setting (i.e. the `null` intiailization and the `increasing` update order) does not outperform.

Indeed, using this simulation setting and $\rho > 0.5$, E-ENET, SCAD, and MCP performs better than MR.ASH.

### Signal setting

We sample the i.i.d. normal coefficients $\beta_j \sim N(0,\sigma_\beta^2)$ for $j \in J$ and $\beta_ j = 0$ otherwise, where $J$ is a set of randomly $s$ indices in $\{1,⋯,p\}$c hosen uniformly at random.

This signal will be called `sparsenormal`.

We fix $s = 20$ throughout this experiment.

### PVE

Then we sample $y = X\beta + \epsilon$, where $\epsilon \sim N(0,\sigma^2 I_n)$.

We fix PVE = 0.5, where PVE is the proportion of variance explained, defined by

$$
{\rm PVE} = \frac{\textrm{Var}(X\beta)}{\textrm{Var}(X\beta) + \sigma^2},
$$
where $\textrm{Var}(a)$ denotes the sample variance of $a$ calculated using R function `var`. To this end, we set $\sigma^2 = \textrm{Var}(X\beta)$.

### Performance Measure

The above two figures display the prediction error. The prediction error we define here is

$$
\textrm{Pred.Err}(\hat\beta;y_{\rm test}, X_{\rm test}) = \frac{\textrm{RMSE}}{\sigma} = \frac{\|y_{\rm test} - X_{\rm test} \hat\beta \|}{\sqrt{n}\sigma}
$$
where $y_{\rm test}$ and $X_{\rm test}$ are test data sample in the same way. If $\hat\beta$ is fairly accurate, then we expect that $\rm RMSE$ is similar to $\sigma$. Therefore in average $\textrm{Pred.Err} \geq 1$ and the smaller the better.

### Packages / Libraries

A list of packages we have loaded is collapsed. Please click "code" to see the list.

```{r library, message = FALSE}
library(Matrix); library(ggplot2); library(cowplot); library(susieR); library(BGLR);
library(glmnet); library(varbvs2); library(ncvreg); library(L0Learn); library(varbvs);
standardize = FALSE
source('code/method_wrapper.R')
source('code/sim_wrapper.R')
```

## Results 

```{r fig1, fig.height=13, fig.width=15}
sdat = readRDS("results/updateorder_rho0.95.RDS")
sdat$fit = factor(sdat$order, levels = c("random","increasing","lasso.path",
                                         "scad.path","lasso.absorder","univar.absorder"))
col = rev(c("skyblue","dodgerblue","limegreen","gold","orange","salmon"))
p1 = my.box2(sdat, "fit", "vobj", cols = col) +
  theme(axis.line    = element_blank(),
        axis.text.x  = element_text(angle = 45,hjust = 1),
        legend.position = "none")
subtitle  = ggdraw() + draw_label("Variational Objective", fontface  = 'bold', size = 18)
p1 = plot_grid(subtitle, p1, ncol = 1, rel_heights = c(0.06,0.95))

p2 = my.box2(sdat, "fit", "pred", cols = col) +
  theme(axis.line    = element_blank(),
        axis.text.x  = element_text(angle = 45,hjust = 1),
        legend.position = "none") +
  scale_y_continuous(trans = "log10", breaks = c(1,1.1,1.2,1.3)) +
  coord_cartesian(ylim = c(1,1.3))
subtitle  = ggdraw() + draw_label("Prediction Error", fontface  = 'bold', size = 18)
p2 = plot_grid(subtitle, p2, ncol = 1, rel_heights = c(0.06,0.95))

p3 = my.box2(sdat, "fit", "time", cols = col) +
  theme(axis.line    = element_blank(),
        axis.text.x  = element_text(angle = 45,hjust = 1),
        legend.position = "none") +
  scale_y_continuous(trans = "log10")
subtitle  = ggdraw() + draw_label("Computation Time", fontface  = 'bold', size = 18)
p3 = plot_grid(subtitle, p3, ncol = 1, rel_heights = c(0.06,0.95))

p4 = my.box2(sdat, "fit", "numiter", cols = col) +
  theme(axis.line    = element_blank(),
        axis.text.x  = element_text(angle = 45,hjust = 1),
        legend.position = "none") +
  scale_y_continuous(trans = "log10")
subtitle  = ggdraw() + draw_label("Number of Iterations", fontface  = 'bold', size = 18)
p4 = plot_grid(subtitle, p4, ncol = 1, rel_heights = c(0.06,0.95))
  
title     = ggdraw() + draw_label("Comparison of Update Orders (log-scale)", fontface = 'bold', size = 20) 
subtitle  = ggdraw() + draw_label("Scenario: EquiCorrGauss + SparseNormal, n = 500, p = 2000, s = 20, pve = 0.5, rho = 0.95", fontface  = 'bold', size = 18) 

fig_main  = plot_grid(p1,p2,p3,p4, nrow = 2, rel_widths = c(0.3,0.3,0.3))
fig       = plot_grid(title,subtitle,fig_main, ncol = 1, rel_heights = c(0.06,0.06,0.95))
fig
```

## Source Code

```{r order}
glmnet_pathorder = function(fit.glmnet) {
  # perform lasso regression and reorder regressors by "importance"
  beta_path = coef(fit.glmnet)[-1,]
  K = dim(beta_path)[2]
  path_order = c()
  for (k in 1:K) {
    crt_path = which(beta_path[,k] != 0)
    if (length(crt_path) != 0 & length(path_order) == 0) {
      path_order = c(path_order, crt_path)
    } else if(length(crt_path) != 0) {
      path_order = c(path_order, crt_path[-which(crt_path %in% path_order)] )
    }
  }
  path_order = unname(path_order)
  index_order = c(path_order, seq(1,dim(beta_path)[1])[-path_order])
  return (index_order)
}

glmnet_absorder = function(beta) {
  return (order(abs(beta), decreasing = TRUE))
}

univar_absorder = function(X, y) {
  colnorm = c(colMeans(X^2))
  return (order(abs(c(t(X) %*% y) / colnorm), decreasing = TRUE))
}
```

```{r code, eval = FALSE}
tdat1        = list()
n            = 500
p            = 2000
s            = 20
sa2          = (2^((0:19) / 20) - 1)^2
method_list  = c("random","increasing","lasso.path","scad.path","lasso.absorder","univar.absorder")
method_num   = length(method_list)
iter_num     = 20
pred         = matrix(0, iter_num, method_num); colnames(pred) = method_list
time         = matrix(0, iter_num, method_num); colnames(time) = method_list
numiter      = matrix(0, iter_num, method_num); colnames(numiter) = method_list
vobj         = matrix(0, iter_num, method_num); colnames(vobj) = method_list


for (i in 1:20) {
  data          = simulate_data(n, p, s = s, seed = i, signal = "normal", rho = 0.95,
                                design = "equicorrgauss", pve = 0.5)
  X             = data$X
  y             = data$y

  fit.lasso        <- cv.glmnet(x = X, y = y, standardize = standardize)
  fit.lasso$beta    = coef(fit.lasso)[-1]
      
  fit.scad         <- cv.ncvreg(X, y, penalty = "SCAD", nfolds = 10)
  fit.scad$beta     = coef(fit.scad)[-1]
      
  lasso.pathorder   = glmnet_pathorder(fit.lasso$glmnet.fit)
  lasso.absorder    = glmnet_absorder(fit.lasso$beta)
  univar.absorder   = univar_absorder(X, y)
  scad.pathorder    = glmnet_pathorder(fit.scad$fit)

  t.mrash1          = system.time(
  fit.mrash1       <- mr_ash_order(X = X, y = y, sa2 = sa2,
                                   stepsize = 1, max.iter = 2000,
                                   standardize = standardize, order = "random",
                                   tol = list(epstol = 1e-12, convtol = 1e-8)))
      
  t.mrash2          = system.time(
  fit.mrash2       <- mr_ash_order(X = X, y = y, sa2 = sa2,
                                   stepsize = 1, max.iter = 2000,
                                   standardize = standardize, order = "increasing",
                                   tol = list(epstol = 1e-12, convtol = 1e-8)))
  t.mrash3          = system.time(
  fit.mrash3       <- mr_ash_order(X = X, y = y, sa2 = sa2,
                                   stepsize = 1, max.iter = 2000,
                                   standardize = standardize, order = "manual",
                                   o = rep(lasso.pathorder, 2000),
                                   tol = list(epstol = 1e-12, convtol = 1e-8)))
  t.mrash4          = system.time(
  fit.mrash4       <- mr_ash_order(X = X, y = y, sa2 = sa2,
                                   stepsize = 1, max.iter = 2000,
                                   standardize = standardize, order = "manual",
                                   o = rep(scad.pathorder, 2000),
                                   tol = list(epstol = 1e-12, convtol = 1e-8)))
  t.mrash5          = system.time(
  fit.mrash5       <- mr_ash_order(X = X, y = y, sa2 = sa2,
                                   stepsize = 1, max.iter = 2000,
                                   standardize = standardize, order = "manual",
                                   o = rep(lasso.absorder, 2000),
                                   tol = list(epstol = 1e-12, convtol = 1e-8)))
      
  t.mrash6          = system.time(
  fit.mrash6       <- mr_ash_order(X = X, y = y, sa2 = sa2,
                                   stepsize = 1, max.iter = 2000,
                                   standardize = standardize, order = "manual",
                                   o = rep(univar.absorder, 2000),
                                   tol = list(epstol = 1e-12, convtol = 1e-8)))
 
  for (j in 1:6) {
    fit           = get(paste("fit.mrash",j,sep = ""))
    pred[i,j]     = norm(data$y.test - predict(fit, data$X.test), '2') / sqrt(500) / data$sigma
    numiter[i,j]  = fit$iter
    vobj[i,j]     = fit$varobj[fit$iter]
    time[i,j]     = get(paste("t.mrash",j,sep = ""))[3]
  }
  
  print(c(vobj[i,]))
}

tdat1 = data.frame(pred = c(pred), vobj = c(vobj), time = c(time),
                   numiter = c(numiter),
                   order = rep(c("random","increasing","lasso.path","scad.path",
                                 "lasso.absorder","univar.absorder"), each = 20))
```

